Gaussian Processes Autoregressive Models for Forecasting the Disturbance Storm Time Index

### 2016-06-05 swsc.tex
Simons changes 2

   \authorrunning{Chandorkar and Camporeale}

   \author{M. Chandorkar
          \inst{1}
          \and
          E. Camporeale\inst{1}
          \and 
          S. Wing \inst{1}
          }

   \institute{Centrum Wiskunde Informatica (CWI), Amsterdam,
              1098XG Amsterdam\\
              \email{\href{mailto:m.h.chandorkar@cwi.nl}{m.h.chandorkar@cwi.nl} \href{mailto:e.camporeale@cwi.nl}{e.camporeale@cwi.nl}} 
             }

   %\institute{Johns Hopkins University, Applied Physics Laboratory, \\ 11100 Johns Hopkins Road, Laurel, Maryland 20723}

>>>>

   \authorrunning{Chandorkar et. al}

   \author{M. Chandorkar
          \inst{1}
          \and
          E. Camporeale\inst{1}
          \and 
          S. Wing \inst{2}
          }

   \institute{\inst{1} Centrum Wiskunde Informatica (CWI), Amsterdam,
              1098XG Amsterdam\\
              \ \email{\href{mailto:m.h.chandorkar@cwi.nl}{m.h.chandorkar@cwi.nl} \href{mailto:e.camporeale@cwi.nl}{e.camporeale@cwi.nl}}\\
              \inst{2} The Johns Hopkins University Applied Physics Laboratory, 
              Laurel, Maryland, 20723, USA
             }
